---
title: "Supplements"
subtitle: "Locus coeruleus modulation of neurophysiological sensory selectivity differs
  in autism and other mental health conditions "
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    latex_engine: xelatex
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
header-includes:
- \usepackage{tocloft}
- \setlength{\cftbeforesecskip}{2pt}
- \setlength{\cftbeforesubsecskip}{1pt}
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# **Abbreviations**
**SEPR** = stimulus-evoked pupillary response   
**BPS** = baseline pupil size   
**MMN** = mismatch negativity   
**ASD** = autism spectrum disorder group   
**CON** = control group   
**MHC** = mental health condition group   

\newpage
```{r setup, include = FALSE, warning = FALSE}
# REQUIRED PACKAGES
require(performance) 
require(lme4) 
require(lmerTest, warn.conflicts = FALSE)
require(emmeans, warn.conflicts = FALSE)
require(ggplot2, warn.conflicts = FALSE)
require(dplyr, warn.conflicts = FALSE)
library(ggpubr, warn.conflicts = FALSE)
library(knitr)
library(kableExtra)
library(stringr)
library(tidyverse)
library(simr)
library(gridExtra)
library(ggpubr)

# PATHS 
if (Sys.info()["sysname"] == "Linux") {
  home_path <- "~"
  project_path <- "/PowerFolders/project_sega"
  data_path <- "/PowerFolders/project_sega/data/AuditoryOddball"
  data_path_eeg <- "/PowerFolders/project_sega/data/AuditoryOddball_EEG"
  datapath <- paste0(home_path, data_path) # .csv + .hdf5 input files
  datapath_eeg <- paste0(home_path, data_path_eeg) # .txt input files (eeg)
  # List all .hdf and .csv files
  data_files <- list.files(path = datapath, full.names = TRUE)
}
if (Sys.info()["sysname"] == "Windows") {
  home_path <- "C:/Users/Nico"
  project_path <- "/PowerFolders/project_sega"
  data_path <- "/PowerFolders/project_sega/data/et auditory oddball"
  data_path_task<-"/PowerFolders/project_sega/data/task auditory oddball"
  data_path_eeg <- "/PowerFolders/project_sega/data/tests/eeg preprocessed auditory oddball"
  datapath <- paste0(home_path, data_path) # hdf5 input files
  datapath_task <- paste0(home_path, data_path_task) # hdf5 input files
  datapath_eeg <- paste0(home_path, data_path_eeg) # .txt input files (eeg)
  # List all .hdf and .csv files
  data_files <- c(list.files(path = datapath, full.names = TRUE),
                  list.files(path = datapath_task, full.names = TRUE))
}
if (Sys.info()["sysname"] == "Darwin") {
  home_path <- "/Volumes/common/"
  project_path <- "/code"
  data_path <- "/code/input/AuditoryOddball/eyetracking"
  data_path_task <- "/code/input/AuditoryOddball/taskdata"
  data_path_eeg <- "/code/input/AuditoryOddball/eeg"
  datapath <- paste0(home_path, data_path) # .hdf5 input files
  datapath_task <- paste0(home_path, data_path_task) # .csv input files
  datapath_eeg <- paste0(home_path, data_path_eeg) # .txt input files (eeg)
  data_path_single_trial_eeg <- "/code/input/AuditoryOddball/eeg_single_trial"
  datapath_single_eeg <- paste0(home_path, data_path_single_trial_eeg)
  # List all .hdf and .csv files
  data_files <- c(
    list.files(path = datapath, full.names = TRUE),
    list.files(path = datapath_task, full.names = TRUE))
}

# Can be used to skip preprocessing and directly read proprocessed data from .rds file:
et_erp_subject <- readRDS(paste0(home_path,project_path,'/data/preprocessed_auditory_ET_ERP_subject.rds'))
et_erp_trial <- readRDS(paste0(home_path,project_path,'/data/preprocessed_auditory_ET_ERP_trial.rds'))
MMN_diff <- readRDS(paste0(home_path,project_path,'/data/preprocessed_auditory_MMN_diff.rds'))
```

```{r, warning=FALSE}
# Renaming the variable "trial" into "stimulus" to match terminology in the paper
names(et_erp_subject)[names(et_erp_subject) == "trial"] <- "stimulus"
names(et_erp_trial)[names(et_erp_trial) == "trial"] <- "stimulus"
```

# Covariates Models
## Supplement 1: Covariates effects on SEPR
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 2: Covariates effects on BPS
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd_low ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 3: Covariates effects on MMN amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 4: Covariates effects on P3a amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 5: Covariates effects on MMN latency
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 6: Covariates effects on P3a latency
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age + verbal_IQ + non_verbal_IQ,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

\newpage
# Main Models on Aggregated Level
## Supplement 7: Model for SEPR
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 8: Model for BPS
```{r, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
lmm <- lmer(
  z_rpd_low ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 9: Model for MMN amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_subject)
anova_table <- anova(lmm)

anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )

kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 10: Model for P3a amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 11: Model for MMN latency
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 12: Model for P3a latency
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + gender + age,
  data = et_erp_subject)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 13: MMN amplitude (difference wave)
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_diff_amplitude ~  manipulation * group * block + (1|SEGA_ID) + gender + age,
  data = MMN_diff)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 14: MMN latency (difference wave)
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_diff_latency ~  manipulation * group * block + (1|SEGA_ID) + gender + age,
  data = MMN_diff)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
# Main Models on Trial Level
## Supplement 15: Model for SEPR
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 16: Model for MMN amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 17: Model for P3a amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_amplitude ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 18: Model for P3a latency
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 19: Model for MMN latency
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_latency ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 20: Model for BPS
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd_low ~ stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 21: Associations of pupillometric measures
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd ~ z_rpd_low * stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))
```

\newpage
## Supplement 22: Associations between pupillometric measures-MMN amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_amplitude ~ z_rpd * z_rpd_low * stimulus *  manipulation * group + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))
```
\newpage
## Supplement 23: Associations between pupillometric measures-P3a amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_amplitude ~ z_rpd * z_rpd_low * stimulus *  manipulation * group + (1|SEGA_ID) + age + gender,
  data = et_erp_trial)
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))
```
\newpage
# Grip Strength Models
## Supplement 24: Grip strength on BPS
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd_low ~ stimulus * group * block * z_grip_strength + (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 25: Grip strength on SEPR
```{r, warning=FALSE}
lmm <- lmer(
  z_rpd ~ stimulus * group * block * z_grip_strength + (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 26: Grip strength on MMN amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_amplitude ~ stimulus * group * block * z_grip_strength + (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 27: Grip strength on P3a amplitude
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_amplitude ~ stimulus * group * block * z_grip_strength + (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
## Supplement 28: Grip strength on MMN latency
```{r, warning=FALSE}
lmm <- lmer(
  z_MMN_latency ~ stimulus * group * block * z_grip_strength+ (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```

## Supplement 29: Grip strength on P3a latency
```{r, warning=FALSE}
lmm <- lmer(
  z_P3a_latency ~ stimulus * group * block * z_grip_strength+ (1|SEGA_ID) + age + gender,
  data = et_erp_subject[et_erp_subject$manipulation == "after", ])
anova_table <- anova(lmm)
anova_table_rounded <- anova_table %>%
  mutate(
    `Sum Sq`   = round(`Sum Sq`, 2),
    `Mean Sq`  = round(`Mean Sq`, 2),
    `NumDF`    = round(`NumDF`, 0),
    `DenDF`    = round(`DenDF`, 0),
    `F value`  = round(`F value`, 2),
    `Pr(>F)`   = round(`Pr(>F)`, 3)
  )
kable(anova_table_rounded) %>%
  kable_styling(latex_options = "scale_down")
```
\newpage
# Miscellaneous
## Supplement 30: Number of included trials per condition
```{r, warning=FALSE}
fun_trials_per_cond <- function(group, variable){
  group_df <- droplevels(et_erp_trial[et_erp_trial$group == group, ])
  # subjects starting with 500 Hz oddball
  ## block 1
  df_before_forward_O500_S750 <- group_df %>% filter(
    (manipulation == "before" & phase == "oddball_block" & stimulus == "oddball" & pitch == "500") |
      (manipulation == "before" & phase == "oddball_block" & stimulus == "standard" & pitch == "750"))
  sample_size <- length(unique(df_before_forward_O500_S750$SEGA_ID))
  max_trials <- sample_size *100
  before_forward_O500_S750 <- paste(round(((sum(!is.na(df_before_forward_O500_S750[variable]), na.rm = T))/max_trials)*100, 2), "%")
  ## block 2
  df_before_reverse_O750_S500 <- group_df %>% filter(
    (manipulation == "before" & phase == "oddball_block_rev" & stimulus == "oddball" & pitch == "750") |
      (manipulation == "before" & phase == "oddball_block_rev" & stimulus == "standard" & pitch == "500"))
  before_reverse_O750_S500 <- paste(round(((sum(!is.na(df_before_reverse_O750_S500[variable]), na.rm = T))/max_trials)*100, 2), "%")
  ## block 3
  df_after_forward_O500S750 <- group_df %>% filter(
    (manipulation == "after" & phase == "oddball_block" & stimulus == "oddball" & pitch == "500") |
      (manipulation == "after" & phase == "oddball_block" & stimulus == "standard" & pitch == "750"))
  after_forward_O500S750 <- paste(round(((sum(!is.na(df_after_forward_O500S750[variable]), na.rm = T))/max_trials)*100, 2), "%")
  # block 4
  df_after_reverse_O750S500 <- group_df %>% filter(
    (manipulation == "after" & phase == "oddball_block_rev" & stimulus == "oddball" & pitch == "750") |
      (manipulation == "after" & phase == "oddball_block_rev" & stimulus == "standard" & pitch == "500"))
  after_reverse_O750S500 <- paste(round(((sum(!is.na(df_after_reverse_O750S500[variable]), na.rm = T))/max_trials)*100, 2), "%")
  # subjects starting with 750 Hz oddball
  ## block 1
  df_before_forward_O750_S500 <- group_df %>% filter(
    (manipulation == "before" & phase == "oddball_block" & stimulus == "oddball" & pitch == "750") |
      (manipulation == "before" & phase == "oddball_block" & stimulus == "standard" & pitch == "500"))
  sample_size <- length(unique(df_before_forward_O750_S500$SEGA_ID))
  max_trials <- sample_size *100
  before_forward_O750_S500 <- paste(round(((sum(!is.na(df_before_forward_O750_S500[variable]), na.rm = T))/max_trials)*100, 2), "%")
  ## block 2
  df_before_reverse_O500S750 <- group_df %>% filter(
    (manipulation == "before" & phase == "oddball_block_rev" & stimulus == "oddball" & pitch == "500") |
      (manipulation == "before" & phase == "oddball_block_rev" & stimulus == "standard" & pitch == "750"))
  before_reverse_O500S750 <- paste(round(((sum(!is.na(df_before_reverse_O500S750[variable]), na.rm = T))/max_trials)*100, 2), "%")
  ## block 3
  df_after_forward_O750_S500 <- group_df %>% filter(
    (manipulation == "after" & phase == "oddball_block" & stimulus == "oddball" & pitch == "750") |
      (manipulation == "after" & phase == "oddball_block" & stimulus == "standard" & pitch == "500"))
  after_forward_O750_S500 <- paste(round(((sum(!is.na(df_after_forward_O750_S500[variable]), na.rm = T))/max_trials)*100, 2), "%")
  ## block 4
  df_after_reverse_O500S750 <- group_df %>% filter(
    (manipulation == "after" & phase == "oddball_block_rev" & stimulus == "oddball" & pitch == "500") |
      (manipulation == "after" & phase == "oddball_block_rev" & stimulus == "standard" & pitch == "750"))
  after_reverse_O500S750 <- paste(round(((sum(!is.na(df_after_reverse_O500S750[variable]), na.rm = T))/max_trials)*100, 2), "%")
  
   trial_per_condition <- data.frame(
     before_forward_O500_S750,
     before_reverse_O750_S500,
     after_forward_O500S750,
     after_reverse_O750S500,
     before_forward_O750_S500,
     before_reverse_O500S750,
     after_forward_O750_S500,
     after_reverse_O500S750)
   t(trial_per_condition)
   }

# Call function for each group for EEG
asd_trials_per_cond_eeg <- fun_trials_per_cond(group = "ASD", variable = "z_MMN_amplitude")
colnames(asd_trials_per_cond_eeg) <- "ASD"
con_trials_per_cond_eeg <- fun_trials_per_cond(group = "CON", variable = "z_MMN_amplitude")
colnames(con_trials_per_cond_eeg) <- "CON"
mhc_trials_per_cond_eeg <- fun_trials_per_cond(group = "MHC", variable = "z_MMN_amplitude")
colnames(mhc_trials_per_cond_eeg) <- "MHC"
# Call function for each group for ET
asd_trials_per_cond_et <- fun_trials_per_cond(group = "ASD", variable = "z_rpd")
colnames(asd_trials_per_cond_et) <- "ASD"
con_trials_per_cond_et <- fun_trials_per_cond(group = "CON", variable = "z_rpd")
colnames(con_trials_per_cond_et) <- "CON"
mhc_trials_per_cond_et <- fun_trials_per_cond(group = "MHC", variable = "z_rpd")
colnames(mhc_trials_per_cond_et) <- "MHC"

condition_table <- cbind(
  asd_trials_per_cond_eeg, con_trials_per_cond_eeg, mhc_trials_per_cond_eeg,
  asd_trials_per_cond_et, con_trials_per_cond_et, mhc_trials_per_cond_et)

condition_trials_table <- kable(
  condition_table, align = "c") %>% 
  kable_classic() %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Eye Tracking" = 3, "EEG" = 3))
condition_trials_table
```
“before_forward_O500_S750” as block 1, oddball 500Hz   
"before_reverse_O750_S500" as block 2 oddball 750 Hz   
"after_forward_O500S750" as block 3 oddball 500 Hz   
"after_reverse_O750S500" as block 4 oddball 750 Hz   
"before_forward_O750_S500" as block 1 oddball 750 Hz   
"before_reverse_O500S750" as block 2 oddball 500 Hz   
"after_forward_O750_S500" as block 3 oddball 750 Hz   
"after_reverse_O500S750" as block 4 oddball 500 Hz

\newpage
## Supplement 31: Post-hoc power analysis
```{r, warning=FALSE, message = FALSE, echo=FALSE, results="hide"}
n_size <- 150 # sample size
k_size <- 4*100 # number of trials --> auditory oddball:
subj <- factor(1:n_size)
trial_id <- 1:k_size # remains integer variable
condition <- c("before", "after")
group <- c("ASD", "MHC", "CON")

subj_full <- rep(subj, k_size)
trial_full <- rep(trial_id, each=n_size)
condition_full <- rep(condition, each=k_size*n_size/2)
group_full <- rep(group, k_size * n_size/3)

covars <- data.frame(id=subj_full, trial=trial_full, condition=condition_full, group=group_full)
fixed <- c(0.1, 0.2, 0.2, 0.2, 0.1, 0.1) # effect sizes
rand <- list(0.05) # random intercept
res <- 1.2 # residual standard deviation

model <- makeLmer(
  y ~ group*condition + (1|id), fixef=fixed, VarCorr=rand, sigma=res, data=covars) # create model
summary(model) # model

power_interaction <- suppressMessages(powerSim(model, nsim=1000, test = fcompare(y ~ group + condition)))
# print(power_interaction)
power_curve_interaction <- powerCurve(model, test = fcompare(y ~ group + condition), along = "id")
plot(power_curve_interaction)
```

```{r, warning=FALSE, results='asis'}
print(power_interaction)
```

\newpage
## Supplement 32: Exploratory model fit for BPS-SEPR association
```{r, warning=FALSE, message = FALSE, echo=FALSE, results="hide"}
# lmer()-, but not poly()-function can handle NAs in the predictors, so
# et_erp_trial_for_model_fit excludes NAs for these exploratory model fit comparisons. 
et_erp_trial_for_model_fit <- na.omit(et_erp_trial[ , c(
  "z_rpd",
  "z_rpd_low",
  "stimulus",
  "manipulation",
  "group",
  "block",
  "SEGA_ID",
  "age",
  "gender")])

# linear
lmm_linear_fit <- lmer(
  z_rpd ~ z_rpd_low * stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial_for_model_fit, REML = F)
anova(lmm_linear_fit)
r2_nakagawa(lmm_linear_fit) 

# quadratic
lmm_quadratic_fit <- lmer(
  z_rpd ~ poly(z_rpd_low, 2) * stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial_for_model_fit, REML = F)
anova(lmm_quadratic_fit)
r2_nakagawa(lmm_quadratic_fit) 
# cubic
lmm_cubic_fit <- lmer(
  z_rpd ~ poly(z_rpd_low, 3) * stimulus * manipulation * group * block + (1|SEGA_ID) + age + gender,
  data = et_erp_trial_for_model_fit, REML = F)
anova(lmm_cubic_fit)
r2_nakagawa(lmm_cubic_fit) 

table_model_compare <- anova(lmm_linear_fit, lmm_quadratic_fit, lmm_cubic_fit)

table_model_compare <- cbind(
  c("linear_fit", "quadratic_fit", "cubic_fit"),
  table_model_compare
)

table_formatted_BPS_SEPR <- table_model_compare %>% 
  kbl(
    col.names = c("","number of parameters",'AIC','BIC','log likelihood','deviance','Chi-squared','df','p-value'),
    row.names = FALSE,
    booktabs = TRUE,
    format = "latex"
  ) %>%
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    full_width = FALSE)
```

```{r, warning=FALSE, results='asis'}
table_formatted_BPS_SEPR
```
AIC = Akaike Information Criterion   
BIS = Bayesian Information Criterion

## Supplement 33: Correlation: block baseline-trial baseline
```{r, warning=FALSE, fig.width=6, fig.height=4}
corr_block_trial_bl <- et_erp_subject %>%
  summarise(
    cor = cor(block_baseline_mean, rpd_low, use = "complete.obs"),
    p_value = cor.test(block_baseline_mean, rpd_low)$p.value,
    conf_low = cor.test(block_baseline_mean, rpd_low)$conf.int[1],
    conf_high = cor.test(block_baseline_mean, rpd_low)$conf.int[2]
  )
print(corr_block_trial_bl)

# Scatter plot with regression line and annotated correlation
ggplot(et_erp_subject, aes(x = block_baseline_mean, y = rpd_low)) +
  geom_point(alpha = 0.6, color = "#0072B2", size = 3) +          
  geom_smooth(method = "lm", se = TRUE, color = "#D55E00") +      
  annotate("text", x = Inf, y = -Inf, 
           hjust = 1.1, vjust = -0.5,
           label = sprintf("r = %.2f, p < .001", corr_block_trial_bl$cor),
           size = 5) +
  labs(
    x = "separate baseline phase",
    y = "BPS") +
  theme_minimal(base_size = 14)
```
